### 2017-10-03 paper.tex
Reverted a sentence I put into rule 5 I don't think we need signposting in such proximity.
Added framing

Despite the success of openness in software development and the curation of Wikipedia,
it is an uncommon approach in academic settings.
Each year,
thousands of university lecturers teach subjects ranging from first year biology,
to graduate-level courses in Indian film.
Some use textbooks written by one or a few authors,
but beyond that,
they develop and maintain their course materials in isolation.
This is curious given that research depends critically on sharing,
and that most researchers complain about how much time teaching takes away from research,
but the sociology and psychology behind this blind spot are out of the scope of this paper.

The authors have many years of experience with community-developed lessons
in the context of research computing in the sciences and humanities
through organizations like Software Carpentry and Programming Historian.
Software Carpentry was founded in 1998 to teach scientists basic computing skills,
and has since spawned two sibling organizations called Data Carpentry and Library Carpentry.
Programming Historian was founded in 2008,
and has evolved into a collaboratively-edited site providing lessons to humanities scholars.
Their guiding principles are that lessons should be:

@@

All open education projects satisfy the first criterion by definition,
but few satisfy the second.
While their lessons are occasionally updated by a small team
(as happens when a new edition of a book is edited and published),
this is not the same as continuous improvement by a large community of contributors.
The ten simple rules that follow summarize what we have learned about doing that
as maintainers, editors, and reviewers of lessons used by tens of thousands of people (Fig. 1, 2).

@@

An example of how to teach these practices is Software Carpentry's instructor training program.
First offered in 2012,
is now a two-day course delivered both in-person and online
\cite{lessons-learned,instructor-training,how-to-teach-programming}.
This program teaches good pedagogical practices,
and introduces everyone who takes it to who Software Carpentry's lessons are for,
how they are delivered,
and how they are maintained.
Largely as a result of this training,
several hundred people per year now contribute to Software Carpentry's lessons.

>>>>

Despite the success of openness in software development and the curation of Wikipedia,
it is an uncommon approach in academic settings.
Each year,
thousands of university lecturers teach subjects ranging from first year biology,
to graduate-level courses in Indian film.
Some use textbooks written by one or a few authors,
but beyond that,
they develop and maintain their course materials in isolation.
This is curious given that research depends critically on sharing,
and that most researchers complain about how much time teaching takes away from research,
but the sociology and psychology behind this blind spot are beyond the scope of this paper.

The authors have many years of experience with community-developed lessons
in the context of research computing in the sciences and humanities,
through organizations like Software Carpentry and Programming Historian.
Software Carpentry was founded in 1998 to teach scientists basic computing skills,
and has since spawned two sibling organizations called Data Carpentry and Library Carpentry.
Programming Historian was founded in 2008,
and has evolved into a collaboratively-edited site providing lessons to humanities scholars.
Their guiding principles are that lessons should be:

@@

All open education projects (e.g. massive open online courses) satisfy the first criterion by definition,
but very few satisfy the second.
In other words,
while it is common for open education projects to be occasionally updated by an individual or small team
(as happens when a new edition of a book is edited and published),
this is not the same as continuous improvement by a large community of contributors.
The ten simple rules that follow summarize what we have learned about doing that
as maintainers, editors, and reviewers of lessons used by tens of thousands of people (Fig. 1, 2).
By following these rules,
we contend that it is possible to create higher quality lessons 
than could be created by an individual or small team,
both in terms of accuracy and pedagogy.
As an added bonus, the lessons are always up-to-date 
and require less time per author to develop and maintain.

@@

An example of how to teach these practices is Software Carpentry's instructor training program.
First offered in 2012,
it is now a two-day course delivered both in-person and online
\cite{lessons-learned,instructor-training,how-to-teach-programming}.
This program teaches good pedagogical practices,
and introduces everyone who takes it to who Software Carpentry's lessons are for,
how they are delivered,
and how they are maintained.
Largely as a result of this training,
several hundred people per year now contribute to Software Carpentry's lessons.
